DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-02 paper/comparison.tex
Minor changes to comparison

Figure~\ref{fig:sys_l2miss} shows the L2 miss rates of DNN control
loop. The key takeaway of this result is that the L2 miss rate is a
poor indicator to the execution time of the control loop. As shown
already, Raspberry Pi 3's increased L2 misses do not fully explain
increase in processing times. In case of Intel UP, as the number of
interfering Bandwidth benchmark instances increases, the L2 miss rates
even drop slightly. In case of TX2 (CPU), from solo to one co-runner,
L2 miss rate increase almost twice, but then the execution time
increase is only about less than 10\%. However, when there are
co-runners, even though the L2 miss rates are largely unchanged, the
DNN processing time increases significantly. TX2 (GPU) also shows
similar behavior. All of these results essentially point to the fact
that DNN inferencing workload is largely memory performance sensitive
but not L2 cache space sensitive.

>>>>

Figure~\ref{fig:sys_l2miss} shows the L2 miss rates of DNN control
loop. The key takeaway of this result is that the L2 miss rate is a
poor indicator to the execution time of the control loop. As shown
already, the Raspberry Pi 3's increased L2 misses do not fully explain
increases in processing times. In case of the Intel UP, as the number of
interfering Bandwidth benchmark instances increases, the L2 miss rates
even drop slightly. In case of the TX2 (CPU), from solo to one co-runner,
L2 miss rate increase almost twice, but then the execution time
increase is a little less than 10\%. However, when there are
co-runners, even though the L2 miss rates are largely unchanged, the
DNN processing time increases significantly. The TX2 (GPU) also shows
similar behavior. All of these results essentially point to the fact
that DNN inferencing workload is largely memory performance sensitive
but not L2 cache space sensitive.
